A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-06-06 introduction.tex
Cite Symbolic Boolean Derivatives as suggested
@pruemmer Please verify that I am not lying here!

Closes: the paper should cite a recent paper in the similar spirit: Symbolic Boolean Derivatives PLDI 21 #24

>>>>

% @Philipp: please verify that this is not a lie!
The problem and our calculus, \Calculus{}, takes a similar approach to the work
of \citeauthor{symbolic-boolean-derivatives}, who present an orthogonal calculus
for handling a similar blow-up in complexity resulting from Boolean combinations
of regular automata in SMT string solvers \cite{symbolic-boolean-derivatives}.
In addition to presenting a decision procedure for lazily dispatching
constraints, we similarly also allow for symbolic labelling of automata to
handle large Unicode alphabets.
